Analysing the three-dimensional structure of P. falciparum

### 2017-07-09 doc/manuscript/paper.tex
Now estimating beta before running PO

@@

In order to integrate

@@

\subsection{Differential analysis}
\note{XXX only possible if Bunnik 2017 paper published.}

>>>>

A number of methods have been proposed to accomplish such tasks, which I will
review in this section.

@@

\citet{ay:three-dimensional}  exploited the 3D models to relate structure to
gene expression. The authors rely on a technic called ``kernelCCA'' with
attempts to find components on different view of the data in such a way that
these are coherent with one another.

@@
